Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-07 paper.tex
More regression results.

Our models are summarized in Table \ref{tab:model}.
Mean min-cut was found to be highly correlated with degree (see Figure \ref{fig:degree-mincut}),
so we exclude min-cut to prevent collinearity.
The high correlation between mean degree and min-cut implies that in most cases
the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
bottlenecks and are thus highly decentralized.

@@

\begin{table*}
\begin{tabular}{llc}
 & Performance$^\dagger$ & Performance$^\dagger$ \\
\hline
Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
Out-Degree Skewness$^\dagger$  &               & \\
Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
Connectivity                   & \+0.02         & \\
Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
Article Count$^\dagger$        &  -0.3          & \\
Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
Revision Count$^\dagger$       & \+0.4          & \\
First Assessment               & \+0.03         & \\
Mean Article Age               &  -0.04         & \\
\hline
DoF                            & 1278           & \\
R$^2$(adj)                       & 0.37           & \\
\end{tabular}
\caption{
\label{tab:model}
}
\end{table*}

>>>>

Our models are summarized in Table \ref{tab:model}.
Mean min-cut was found to be highly correlated with degree (see Figure \ref{fig:degree-mincut}),
so we exclude min-cut to prevent collinearity.
The high correlation between mean degree and min-cut implies that in most cases
the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
bottlenecks and are thus highly decentralized.
In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
once with in-degree skewness and once with out-degree skewness.

@@

\begin{table*}
\small
\begin{tabular}{lllllllll}
                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
\hline
Mean degree$^\dagger$          &  -0.8$^{***}$  &  -0.8$^{***}$
                               &  -0.6$^{**}$   &  -0.8$^{***}$
                               &  &
                               &  & \\
In-degree skewness$^\dagger$   &  -0.6$^{***}$  & \+ ---      
                               &  -0.4$^{**}$   & \+ ---      
                               &  & \+ ---      
                               &  & \+ ---      \\
Out-degree skewness$^\dagger$  &  \+ ---        & -0.5$^{***}$  
                               &  \+ ---        & -0.6$^{***}$
                               &  \+ ---        &
                               &  \+ ---        & \\
Mean path$^\dagger$            &  -0.36$^{***}$ & -0.36$^{***}$ 
                               &  -0.03         & -0.10
                               &  &
                               &  & \\
C-eff$^\dagger$                &  -0.08$^{**}$  & -0.08$^{**}$  
                               &  \+ ---        & \+ ---      
                               &  \+ ---        & \+ ---      
                               &  \+ ---        & \+ --- \\
Connectivity                   & \+0.02         & \+0.02        
                               &  \+0.08        & \+0.09
                               &  &
                               &  & \\
Mean editors/article$^\dagger$ & \+0.4$^{***}$  & \+0.4$^{***}$ 
                               & \+0.2          & \+0.3
                               &  &
                               &  & \\
Article count$^\dagger$        &  -0.3          & -0.3          
                               & \+0.6${^*}$    & \+0.7${^*}$ 
                               &  &
                               &  & \\
Editor count$^\dagger$         & \+0.7$^{*}$    & \+0.5         
                               & \+0.7$^{*}$    & \+1.0$^{**}$
                               &  &
                               &  & \\
Revision count$^\dagger$       & \+0.4          & \+0.4         
                               &  -0.8$^{**}$   & -0.9$^{**}$
                               &  &
                               &  & \\
First assessment               & \+0.03         & \+0.06        
                               & \+0.09$^{*}$   & \+0.10$^{**}$
                               &  &
                               &  & \\
Mean article age               &  -0.04         & -0.03         
                               &  -0.04         & -0.04
                               &  &
                               &  & \\
\hline
DoF                            & 1278           & 1278          
                               & 1048           & 1048
                               &  &
                               &  & \\
R$^2_{adj}$                    & 0.37           & 0.37          
                               & 0.15           & 0.16
                               &  &
                               &  & \\
\end{tabular}
\caption{
\label{tab:model}
}
\end{table*}
